## Ensembles

Ensembles are collections of `ml_model` objects that are used together to make predictions.

An ensemble can consist of a single model. Using the `m_lm_x1` model defined in the previous section as an example,

```{r}
e_lm_1 <- ml_ensemble() + m_lm_x1
e_lm_1
```

This construction first creates an empty ensemble using `ml_ensemble()` and then adds an existing model into the ensemble. The ensemble can be used with `predict` as before,

```{r}
predict(e_lm_1, data_test)
```

Because this ensemble consists of a single model, the predictions are equivalent to results in the previous section.

However, a key characteristic of ensembles is their support for multiple models. In the present context, it is possible to train a new model on the `x2` variable of the synthetic dataset and create an ensemble of two models,

```{r}
m_lm_x2 <- ml_model(lm(y ~ x2, data=data_train), name="lm_x2")
e_lm_2 <- m_lm_x1 + m_lm_x2
e_lm_2
```
A similar result can be achieved by extending the existing ensemble with the new model,

```{r}
e_lm_2 <- e_lm_1 + m_lm_x2
e_lm_2
```

Predictions using the new ensemble are different,

```{r, warning=TRUE}
predict(e_lm_2, data_test)
```
Importantly, the above command generates a warning. This signals that the ensemble is taking unchecked assumptions during the prediction, which can be addressed by calibration.

