## Hooks

Hooks are functions that are executed at predefined points in a pipeline.
In the context of a machine learning pipelines, such functions can be used to
pre-process data before applying a machine learning model, or to post-process
outputs.

As an example, consider that future data may be supplied in a different format
with variables denoted as `X1` and `X2` instead of the names `x1` and `x2` used
for training.

```{r}
uppercase_data <- data.frame(
  X1 = seq(1, 4) + rnorm(4, 0, 0.2),
  X2 = seq(1, 4) + rnorm(4, 0, 0.2)
)
```

Direct application models trained on dataset with variables `x1` and `x2` is
bound to give either errors or incomplete outputs. For example,

```{r}
predict(e_lm_calib, uppercase_data)
```

To make prediction on such new datasets, the data should be adjusted before
performing the prediction. This transformation can be incorporated into an
`ml_model` or `ml_ensemble` via a hook.

```{r}
df_lowercase <- function(x) {
  colnames(x) <- tolower(colnames(x))
  x
}
hook_df_lowercase <- ml_hook(df_lowercase, type="pre")
hook_df_lowercase
```

The function `df_lowercase` takes one argument and returns one object. The
hook object `hook_df_lowercase` is defined specifying that `df_lowercase`
should be used as pre-processing step.

A list of hooks can be attached to a model in the `ml_model` constructor.

```{r}
e_models_with_hooks <-
  ml_model(lm(y ~ x1, data=d), name="lm_x1", hooks=list(hook_df_lowercase)) +
    ml_model(lm(y ~ x2, data=d), name="lm_x2", hooks=list(hook_df_lowercase))
```

This construction is reasonable if models require different sets of pre- and
post-processing steps. When a step can be applied just once, then a hook can
be associated with the ensemble instead.

```{r}
e_with_hooks <- ml_ensemble(hooks=list(hook_df_lowercase)) +
        ml_model(lm(y ~ x1, data=d), name="lm_x1") +
        ml_model(lm(y ~ x2, data=d), name="lm_x2")
e_with_hooks_calib <- calibrate(e_with_hooks, calib_data, label=calib_data$y)
predict(e_with_hooks_calib, uppercase_data)
```

Thanks to the pre-processing transformation, the ensemble generates predictions
even though the new data is not in the same format as the training data.

For further details on how to define hooks, see `help(ml_hook)`. For details
on how to attach hooks, see `help(ml_model)` and `help(ml_ensemble)`.
