## Models

The package manages machine learning models using objects of class `ml_model`. These objects are constructed using the `ml_model` constructor. As a minimal example, consider a linear regression trained on the synthetic dataset.

```{r, eval=TRUE, echo=TRUE}
lm_x1 <- lm(y ~ x1, data=data_train)
m_lm_x1 <- ml_model(lm_x1)
```

The first object, `lm_x1`, is a standard R model. The second line defined an `ml_model` object that contains the R model. They behave similarly in terms of making predictions. For example,

```{r, eval=TRUE, echo=TRUE}
data_test <- data.frame(x1 = c(1, 2, 3, 4),
                     x2 = c(1, 2, 3, 4))
predict(lm_x1, data_test)
predict(m_lm_x1, data_test)
```
A very brief description of the `ml_model` object is available via `print`.

```{r}
m_lm_x1                   ## equivalent to print(m_lm_x1)
```
The above displays the 'name' of the model, which in this case is 'lm_x1' because it was inferred from the constructor. It is possible to set the name to another string within the constructor, for example,

```{r}
ml_model(lm_x1, name="my_model")
```
The model name is important when several models are joined into an ensemble.

