## Setup

The vignette relies on package `mlensemble`.

```{r, eval=TRUE, echo=TRUE}
library(mlensemble)
```

Examples refer to a regression task based on a small synthetic dataset. Consider a variable `x` with linear relationships to variables `x1`, `x2`, and `y`. Consider that `x` is not observable, and that training data consist of noisy measurements of the other quantities.

```{r, eval=TRUE}
x <- seq(0, 10, length=21)
data_train <- data.frame(
  x1 = x + rnorm(length(x)),
  x2 = x + rnorm(length(x)),
  y = x + rnorm(length(x))
)
head(data_train, 4)
```

The regression task is to predict `y`. Both `x1` and `x2` are correlated with `y` and can be used individually to predict `y`. They can also be used together.

Given only information in `d`, it can be argued that a linear regression on both `x1` and `x2` would be suitable. However, if future data is likely to have slightly different properties, then this recommendation may not hold. For example, if `x2` is likely to carry considerable noise in the future, then it may be better to use `x1` and `x2` in a more flexible manner.
