---
title: Ensembles of Machine Learning Models
output:
  rmarkdown::html_vignette:
    toc: true
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{Consonance testing}
  %\usepackage[UTF-8]{inputenc}
---

```{r, child=file.path("sections", "styles.Rmd")}
```


## Synopsis

Package `mlensemble` provides a framework for managing ensembles of machine
learning models. Importantly, the framework does not train or evaluate
individual models. It only provides an interface for putting existing models
together into ensembles. The framework is agnostic to the implementation details
of individual models. This approach allows ensembles to have heterogeneous
components such as models trained, for example, on different training datasets
or with different feature sets. At the same time, the framework allows for
ensemble calibration. This offers opportunities to tune how individual models
come together to form integrated predictions.


```{r, child=file.path("sections", c("introduction.Rmd", "setup.Rmd", "models.Rmd", "ensembles.Rmd", "calibration.Rmd", "hooks.Rmd", "descriptions.Rmd"))}
```


## Appendix {#appendix}

```{r}
sessionInfo()
```

